LAGOS lake depth

### 2020-01-24 figures/02_depth_model.Rmd
add oliver 2016 figures

ggplot() +
  geom_boxplot(data = dt$no_shape, aes(y = resid, x = shape_class),
               outlier.shape = NA) +
  ylim(-20, 20)

>>>>

ggplot() +
  geom_boxplot(data = dt$no_shape, aes(y = resid, x = shape_class),
               outlier.shape = NA) +
  ylim(-20, 20)
```

```{r 02_depth_oliver, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=3.4}
# setwd("figures")
oliver2015 <- LAGOSNE::lagos_load_oliver_2015() %>%
  mutate(lake_maxdepth_m_oliver = zmaxpredict)
dt <- readRDS("../data/01_depth_model/oliver_model.rds")

rmse_group <- group_by(dt$test, hu4_zoneid) %>%
  summarize(r_rmse = yardstick::rmse_vec(
    exp(lake_maxdepth_m), 
    exp(lake_maxdepth_m_predicted)) / mean(lake_maxdepth_m))
hu4_gis <- st_read("../data/gis.gpkg", layer = "hu4s_focal_simple") %>%
# ggplot() + 
#   geom_sf(data = hu4_gis) +
#   geom_sf_text(data = hu4_gis, aes(label = hu4_zoneid))
  left_join(rmse_group) %>%
  dplyr::filter(!is.na(r_rmse) & r_rmse != Inf & r_rmse < 12)
ggplot() +
  geom_sf(data = hu4_gis, aes(fill = r_rmse))

## predicted vs obs
ggplot(data = dt$test) + 
  geom_point(aes(x = lake_maxdepth_m_predicted, 
                 y = lake_maxdepth_m)) +
  geom_abline(aes(slope = 1, intercept = 0))

## calculate metrics
gridExtra::grid.arrange(gridExtra::tableGrob(
bind_rows(yardstick::rmse(dt$test, 
                          exp(lake_maxdepth_m), exp(lake_maxdepth_m_predicted)), 
          yardstick::rsq(dt$test,
                         exp(lake_maxdepth_m),
                         exp(lake_maxdepth_m_predicted)))))

## replication vs oliver
# dt$test <- dt$test %>%
#   left_join(dplyr::select(dplyr::mutate(oliver2015, lagoslakeid = as.character(lagoslakeid)), lagoslakeid,
#                           lake_maxdepth_m_oliver))
# ggplot(data = dt$test) + 
#   geom_point(aes(x = exp(lake_maxdepth_m_predicted), 
#                  y = lake_maxdepth_m_oliver)) +
#   geom_abline(aes(slope = 1, intercept = 0))

cowplot::plot_grid(
  ggplot(data = oliver2015) +
    geom_point(aes(x = zmaxpredict, y = zmaxobs)) +
    geom_abline(aes(slope = 1, intercept = 0)), 
  ggplot(data = oliver2015) +
    geom_point(aes(x = log(zmaxpredict), y = log(zmaxobs))) +
    geom_abline(aes(slope = 1, intercept = 0))
)
```
